Autonomous Oceanographic Data Collection Estimating Excursion Sets of Vector-valued Gaussian Random Fields

### 2020-06-25 ans_to_reviewers/answers-to-reviewers.tex

\reply: The traditional entropy calculations for this GP aim to reduce the log determinant of the updated covariance matrix at the grid locations. It will not vary with the data realizations, so in our setting this information criteria will always give the same path. The EIBV criterion is aligned with our ES motivation for this study. When focusing on the expected EIBV, the paths will vary with the data as we see in our simulation study and in the real-data example. We see this as a clear benefit of the approach compared with entropy-based calculations. Still, sampling approaches using hybrid criteria or multi-attribute criteria might balance goals in such situations, but we leave that for future research. (This is briefly mentioned as further work in Closing remarks.)

@@

\item{\revcom  :}\label{r1c9}

On the issue of covariance separability, objections have always been raised when I have used it as its unrealistic. My rejoinder has always worked, that of citing the “all models are wrong”, George Box’s famous phrase. But what I was able to show in each case is a cross-validatory assessment that showed the model was “useful”. I wonder if such a model assessment could be made here to support the assumption of separability and other things as well. By the way, in spatial mapping at least, point predictors are pretty robust against mis-specification of the covariance. Where things go sideways is in the confidence bands or ellipsoids they produce. What are the error bands when modelling binary responses? Surely the predicted plumes have fuzzy boundaries.

\reply: At this spatial scale there is often not so much data to infer a detailed statistical model, and this is the reason for our parsimonious model in the real-data case. In other related situations, for instance that of larger fjord or ocean fronts, which are at a larger scale, there would usually be more data available for instance in the form of satellite data or from computer model simulations. (We added references to related papers that explored non-stationary Gaussian models for oceanographic phenomena at a larger scale than what is used here.) That said, we do provide some validation of the model via residual analysis. Moreover, the main contribution of this paper is on design more than modeling. In the online resources with open-source code, there are demos using more complex covariance models (non-stationary variance and non-isotropic random fields).

We agree that more complex models would matter more if we step up to a criterion such as volume calculations.

@@

\item{\revcom  :}\label{r1c10}

The strategy at the bottom of page 17 seems ad hoc. Could you not use the data collected with the two ahead design to get better estimates of parameters and then with these parameters and thereafter a better myopic design?

\reply: We have chosen not to explore any re-estimation of parameters. The resources onboard do not allow such computationally demanding evaluations. Overall, we believe the capabilities and limitations of the AUV are clarified in the revised version of the paper.

@@

\item{\revcom :}\label{r1c11}

Are these results generalizable? In other words, how much plume-to-plume variability is there? One of the problems with modelling using a lot of parameters, is there instability over replicate experiments. To put it another way which model parameters represent plume-population parameters and which represent random plume effects?

\reply: We agree that this is a simple model for plume temperature and salinity variation. However, it is not common to have ocean model data or satellite data at this spatial resolution, which would be required for training. So rather than overfitting, we have chosen a parsimonious model.

@@

\item{\revcom :}\label{r1c12}

The separability assumption is to be relaxed in future work. Should publication of this case study await the proposed improvement? It would make for a much better paper.

\reply: There are ongoing efforts to provide high-resolution ocean models which would be required for such detailed model specification. But as pointed out above, we believe that spatio-temporal variations would be a more realistic extension, especially if repeated satellite data or ocean modeling is available. The methodological approach for sampling designs, which is the main contribution of the current paper, would however still be the transferable.

@@

\item{\revcom : (specific comments)}\label{q11}

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item “joint excursion sets” in the title would be a turnoff for most statisticians. Having read the paper pretty carefully I still am not sure why they are so labelled.\par
\reply: We avoid the term' joint excursion sets' in the revised version. The revised version build on a more general notation, but link to the ES for temperature and salinity whenever it is appropriate to exemplify concepts and show results.

@@

\reply: We removed this Figure in the revision.

\vspace{1em}

\item Why are the ES’s called ”excursion sets? Why excursion probabilities?\par

\reply: The revised Section 2 contains a general formulation for random sets, which is then exemplified by our ESs for the multivariate process. In the Introduction and Section 2 we motivate the ES for multivariate processes for this application. In many applications it is important to find zones with joint high values of many variables.

\item I did not spot a definition for the “waypoint graph” a phrase used several times in the paper. Again points to the need to identify the audience. I doubt that most statisticians would know that phrase.\par
\reply: The waypoint graph is clarified in the revised version.  
\vspace{1em}

@@

\item I did not spot a definition for the “waypoint graph” a phrase used several times in the paper. Again points to the need to identify the audience. I doubt that most statisticians would know that phrase.\par
\reply: The waypoint graph is clarified in the revised version.  
\vspace{1em}

\item In statistics journals, random variables are commonly labelled by Roman characters e.g. Z, parameters in Greek e.g. $\xi$. I realize that in other scientific domains that distinction is not always made but I do recommend the change if the paper is to appear in a stats journal.\par

\reply: We use $Z$ for the random field in the revised version.
\vspace{1em}

\item There is not much of novelty in the Gaussian Process theory used in the paper- its pretty much standard. I suggest that the derivations stated in detail be summarized by just the results. Statisticians will know these things and users will not care.\par
\reply: We collapsed the previous sections 3, 4 and 5 to new Section 2 and 3 containing the statistical novelty on EIBV closed-form expressions. The proofs are in a new Appendix.

@@

\end{itemize}

\end{answers}

% \newpage

%======================================================================
\section*{Answers to referee 2}
%======================================================================
All comments of Reviewer 2 are listed below and answered on a point-by-point basis.

@@

I know very little about the AUVs you discuss, and I suspect many of your readers will be in a similar position. Additional contextual information would be helpful

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[2.1.1] What sort of onboard computing do they have? It may not be something like an Intel 2.1 GHz, 4-thread processor, but a more informative description of something most readers relate to would be helpful. Similar information related to RAM and hard drive space would be helpful. What are the computational limits of these machines?\par

\reply: We have clarified information about AUVs and their computational capabilities in Section 4. 
It is a multicore GPU NVIDIA Jetson TX1 (quad-core 1.91 GHz 64-bit ARM machine, a 2-MB L2 shared cache, and 4 GB of 1600 MHz DRAM). 
\vspace{1em}

@@

\item[2.1.2] How long do the AUVs typically explore in one go? Is there a minimum/maximum time?\par

\reply: Maximum speed and payload are limiting coverage. This ranges to minutes to 24h for larger crafts. Time constraints for operations are typically related to costs of ship time and man-hours during operation.  
\vspace{1em}

@@

\item[2.1.3] What kind of movements can the AUVs make? Chess-like moves (horizontal, vertical, diagonal)?\par

\reply: AUVs as in our application are free to move in 6 degrees of freedom on the triangulated graph. This is shown in Fig.1 and Fig. 4 with the waypoint graph. (They are essentially flying under water. In oceanographic application they also perform yo-yo movements in depth.) 
\vspace{1em}

@@

\item[2.1.4] Is there a minimum/maximum number of points you want to sample?\par

\reply: The coverage available is usually limited by man-hours to follow operations, but for large-time operation also on battery capacity. The important question here is "How do one prioritize the correct points to visit?", which is central to the development of the EIBV and the application shown in the paper. 
\vspace{1em}

@@

\end{itemize}

\item{\revcom :}\label{r2c2}

p. 9, Eq. (8): the dependency on $\bx$ and $\bx'$ has been omitted for some of the parameters without mention. Or are the parameters constant across locations?

\reply: In the revised version the notation has been improved. There is limited data for training in our case, so there is a linear regression trend while covariance parameters have been set constant across locations.

@@

\reply: We agree that this is a simplified model. However, one would need high-resolution ocean model data or satellite information to fit a more complex model. But in the accompanying code we run cases with more complex covariances, so the interested user can test if / how it matters for the design. We believe spatio-temporal models would be a very interesting next step and present that as further work.

\item{\revcom  :}\label{r2c4}

p. 9, Eq. (10). Are the temperature and salinity processes at a specific location effectively independent of one another? (I truly don’t know). That is what is implied by Eq. (10).

\reply: The temperature and salinity are dependent in the GRF model. But the temperature and salinity data are collected from different instruments, and we assume that they are conditionally independent, given the GRF variables. That said, other measurements might be extracted or processed from common sensor readings and would then be conditionally dependent. We mentioned this briefly in the model description.

@@

\item{\revcom :}\label{r2c5}

p. 9, Eq. (11). The form of the equation is reminiscent of the Sherman-Morrison-Woodbury solution for fixed-rank kriging. $\bSigma$ may not be small here, but I wonder if there may be a computational advantage to considering an alternative computational solution.  See e.g., Cressie, N. and Johannesson, G. (2008), Fixed rank kriging for very large spatial data sets. Journal of the Royal Statistical Society: Series B (Statistical Methodology), 70: 209-226. doi:10.1111/j.1467-9868.2007.00633.x.

\reply: The update formula assimilates relatively modest data sizes at each waypoint. Moreover, only the near-surface grid is considered here (two dimensional spatial domain). This means that the computational requirements are mainly driven by the number of combinations for sampling designs, not the size of the domain or the data dimension. 
We still agree that computational approximations, such as fixed-rank-kriging, would be useful for larger-size three dimensional applications.

@@

\item{\revcom  :}\label{r2c6}

p. 9, Eq. (13). Why does $\bm$ have a distribution before seeing the data? I can see how $\bm(\by)$ would have a distribution since it depends on $\by$. It almost feels Bayesian, but nothing indicates that this analysis is being pursued from a Bayesian perspective. Why is it valid for $\bm$ to have a distribution prior to seeing data?

\reply: These parts of the paper are largely rewritten. We have generalized the closed-form solutions. (See point 2 and 3 at the start of reply letter.) The main body should contain results of general interest as well as provide insight about the statistical novelty. The proofs are now in Appendix with a succinct notation.

@@

\reply: We have generalized the closed-form solutions. (See reply above.)

\item{\revcom :}\label{r2c12}

This method relies on computing the marginal probabilities in each grid cell. This is computationally convenient and is likely required because of the limited computing power of the AUVs. However, the optimization should technically be performed with respect to the joint distribution across all grid cells. While the context may not allow this in practice, it would be helpful to get an idea of how much error is introduced by this approximation. I recommend creating a small but realistic-as-feasible simulation study comparing the accuracy of the probabilities, a comparison of the computational expense, and examining if/how navigation decisions change based on whether one uses the marginal/joint computations.

\reply: In the revised version we provide closed-form solutions to more general criteria (beyond the EIBV), such as volume calculations involving coupling between locations. But as you mention, the real-world application has computational limitations, and we still use marginals in the examples.

@@

\item{\revcom :}\label{r2c13}

Fig. 7 is difficult to understand. The goal is to show the various paths taken by the AUV in the
simulation example. But it is very difficult to determine which paths are very common and which
are uncommon. Some ideas that may make this graphic more useful:

\begin{quote}
-Don’t worry about the paths but focus on the nodes visited. Represent each node using a circle or hexagon.\par
-Make the node shading darker depending on whether that node is visited in a
simulation. Nodes with no visits would be white. Nodes with 100 visits would be black.\par
-The true excursion set is a random variable, but it would be informative to overlay the
average position of the excursion set over each of the panels so the reader can see how
the simulated AUV moves back and forth across the excursion set.
\end{quote}

\reply: We have removed this figure because it confused the explanation. The online resources contain movies of sampling paths, and the code allows users to generate sampling results by themselves.

@@

\item{\revcom :}\label{r2c14}

While the context does not allow full reproducibility of the paper results, no implementation details are provided. What software was used to perform the bulk of analysis? Are there scripts available that can be adapted by others for similar purposes? Please provide resources for the practical implementation of the methodology discussed in the paper.

\reply: Code is improved in the revision and provided for open-source usage: \url{https://cedrictravelletti.github.io/Submarine/}.

@@

\item{\revcom - Major 1:}\label{r3c1}

I think this is an interesting paper. The paper is well written, 
and the authors have motivated the application well. 
The authors indicate several paths forward for work in this area, which I think pose interesting questions. They may want to elaborate a bit more on those.

\reply: In the revised 'Closing remarks', we elaborate more on computational approximations required for three-dimensional way-point graphs and space-time modeling including relevant references \citep{sigrist2015stochastic,richardson2017sparsity}, on using more complicated criteria for the data collection, and thoughts related to finite horizon optimization where there has been much creative work in the robotics literature including probabilistic road maps and rapidly-exploring random trees \citep{karaman2011sampling} whose statistical properties are not yet clear.

We have also strengthened the discussion on communication for the AUV. In doing so, we relate the topics of autonomy and communication to the modeling and computational assumptions that applies to this paper. With the possibilities of wifi communication to a mother-ship at waypoints, more advanced modeling and computational routines are possible, of course with new challenges related to design and planning for when and where this communication should occur. This topic has caught much interest in control engineering \citep{zolich2019survey}, and statistical evaluations could contribute in this setting.

@@

\reply: This is changed in the revised version.

\item{\revcom - Major 2:}\label{r3c3}

Figure 4: Why not show excursion probabilities for, say, myopic selection as well?

\reply: These plots are changed in the revised version.

In the accompanying code (\url{https://cedrictravelletti.github.io/Submarine/} )
there are showing various sampling results and for displaying other outputs if the reader is interested in comparing results with for instance univariate excursion probabilities.
